Binning Strategies and Related Loss for Large Data

### 2015-04-17 Paper.Rnw
Add description of how many hidden points exist in the traditional histogram for the coarse data

<<SimDataScatterplots,echo=F,include=T,eval=T,fig.width=8, fig.height=5.5, out.width='.8\\linewidth', fig.pos='h',fig.align='center',tidy=F, cache=TRUE, fig.show='hold',fig.cap="Scatterplots of fine and coarse versions of the simulated bivariate data. \\hh{include a finding here- e.g. how big is the loss under each scenario?}">>= 
### Try 2d binning with MVN data
n=100000
set.seed(31415)
unifdat <- data.frame(x= runif(n, min=0, max=100),
                      y= runif(n, min=0, max=100),
                      type="Uniform",
                      record = "Fine")
normdat <- data.frame(x= rnorm(n, mean=50, sd=11),
                     y= rnorm(n, mean=50, sd=11),
                     type="Normal",
                     record = "Fine")
expdat <- data.frame(x= rexp(n, .11),
                     y= rexp(n, .11),
                     type="Exponential",
                     record = "Fine")
datlist <- list(unifdat,normdat,expdat)
### round all data to resolution alpha
alpha <- 2
for(i in 1:3){
  datlist[[i]]$roundx <- ((datlist[[i]]$x + 1)%/%alpha)*alpha
  datlist[[i]]$roundy <- ((datlist[[i]]$y + 1)%/%alpha)*alpha
}

>>>>

<<SimDataScatterplots,echo=F,include=T,eval=T,fig.width=8, fig.height=5.5, out.width='.8\\linewidth', fig.pos='h',fig.align='center',tidy=F, cache=TRUE, fig.show='hold',fig.cap="Scatterplots of fine and coarse versions of the simulated bivariate data. In the coarse data 97.4\\%, 98.7\\% and 99.1\\% of the points are completely hidden behind at least one other point due to over-plotting in the uniform, normal and exponential data, respectively.">>= 
### Try 2d binning with MVN data
n=100000
set.seed(31415)
unifdat <- data.frame(x= runif(n, min=0, max=100),
                      y= runif(n, min=0, max=100),
                      type="Uniform",
                      record = "Fine")
normdat <- data.frame(x= rnorm(n, mean=50, sd=11),
                     y= rnorm(n, mean=50, sd=11),
                     type="Normal",
                     record = "Fine")
expdat <- data.frame(x= rexp(n, .11),
                     y= rexp(n, .11),
                     type="Exponential",
                     record = "Fine")
datlist <- list(unifdat,normdat,expdat)
### round all data to resolution alpha
alpha <- 2
for(i in 1:3){
  datlist[[i]]$roundx <- ((datlist[[i]]$x + 1)%/%alpha)*alpha
  datlist[[i]]$roundy <- ((datlist[[i]]$y + 1)%/%alpha)*alpha
}

# # Find % hidden points in coarse data
# unifPercHidden <- (100000 - nrow(unique(datlist[[1]][,c("roundx","roundy")]))) / 100000
# normPercHidden <- (100000 - nrow(unique(datlist[[2]][,c("roundx","roundy")]))) / 100000
# expoPercHidden <- (100000 - nrow(unique(datlist[[3]][,c("roundx","roundy")]))) / 100000
